---
title: "Plots and spatial autocorrelation analysis"
author: "Justina Razanauskaite"
date: "2024-06-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the packages:

```{r}
pacman::p_load(tidyverse, raster, sf, ggplot2, dplyr, gridExtra, tmap, cowplot, cartogram, spdep, knitr, kableExtra, webshot2, magick)
```

Load in the pre-processed (statistical) data:

```{r}
df <- read_csv("../data/df_final.csv")
df <- df[,-1]
```

## Load municipalities:

Loading the data from GADM - Global Administrative Areas database.

```{r}
# Load the data:
mun <- st_read("../data/gadm41_DNK_2.json")

# Set the CRS:
mun <- mun %>% 
  st_as_sf() %>% 
  st_transform(crs = 25832) 

# Simple municipality plot:
#plot(st_geometry(mun))

# Renaming the municipalities so that they would match the ones in the statistical data:
mun$NAME_2[31] <- "Aarhus"
mun$NAME_2[25] <- "Copenhagen"
mun$NAME_2[60] <- "Vesthimmerlands"
mun$NAME_2[21] <- "Høje-Taastrup"
```

## Aggregating data by municipality, with total number of top 5 municipalities:

The following code shows top five municipalities according to total number of newcomers to Denmark for years 2020-2023.

In all these plots, top-5 municipalities remain the same:
- Copenhagen
- Aarhus
- Aalborg
- Odense
- Frederiksberg

```{r}
#------------------2020------------------
aggregated_data_2020 <- df %>%
  filter(year == 2020) %>%                 # Filter by year
  group_by(municipality) %>%               # Group data by municipalities
  summarise(total = sum(n)) %>%            # Calculate the total number of newcomers for each municipality
  arrange(desc(total))                     # Arrange the data into descending order
aggregated_data_2020$year <- 2020          # Save an index for a year

# Selecting top 5:
aggregated_data_2020_t <- aggregated_data_2020[1:5, ]

#------------------2021------------------
aggregated_data_2021 <- df %>%
  filter(year == 2021) %>%
  group_by(municipality) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))
aggregated_data_2021$year <- 2021

aggregated_data_2021_t <- aggregated_data_2021[1:5, ]

#------------------2022------------------
aggregated_data_2022 <- df %>%
  filter(year == 2022) %>%
  group_by(municipality) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))
aggregated_data_2022$year <- 2022

aggregated_data_2022_t <- aggregated_data_2022[1:5, ]

#------------------2023------------------
aggregated_data_2023 <- df %>%
  filter(year == 2023) %>%
  group_by(municipality) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))
aggregated_data_2023$year <- 2023

aggregated_data_2023_t <- aggregated_data_2023[1:5, ]

# The code below combines all data sets with total number of newcomers across Top-5 municipalities, 2020-2023:
top_5_aggregated <- rbind(aggregated_data_2020_t, 
                          aggregated_data_2021_t, 
                          aggregated_data_2022_t, 
                          aggregated_data_2023_t)

top_5_aggregated$year <- as.factor(top_5_aggregated$year)
```

## Plot these results as a histogram for each year:

```{r}
#------------------2020 Top-5 municipalities ------------------

plot_1 <- aggregated_data_2020_t %>%
  ggplot(aes(x = reorder(municipality, -total), 
             y = total)) +
  geom_bar(stat = "identity", 
           fill = "#8B4513") + 
  geom_text(aes(label = total), 
            vjust = -0.3, 
            size = 2.5) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 14000, by = 1000)) +
  labs(x = "Municipality", 
       y = "Total Number of Newcomers", 
       title = "Top 5 Municipalities by Newcomers, 2020") +
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold"),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank())

#------------------2021 Top-5 municipalities ------------------

plot_2 <- aggregated_data_2021_t %>%
  ggplot(aes(x = reorder(municipality, -total), 
             y = total)) +
  geom_bar(stat = "identity", 
           fill = "#CD853F") + 
  geom_text(aes(label = total), 
            vjust = -0.3, 
            size = 2.5) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 14000, by = 1000)) +
  labs(x = "Municipality", 
       y = "Total Number of Newcomers", 
       title = "Top 5 Municipalities by Newcomers, 2021") +
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold"),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank())

#------------------2022 Top-5 municipalities ------------------

plot_3 <- aggregated_data_2022_t %>%
  ggplot(aes(x = reorder(municipality, -total), 
             y = total)) +
  geom_bar(stat = "identity", 
           fill = "#D2B48C") + 
  geom_text(aes(label = total), 
            vjust = -0.3, 
            size = 2.5) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 14000, by = 1000)) +
  labs(x = "Municipality", 
       y = "Total Number of Newcomers", 
       title = "Top 5 Municipalities by Newcomers, 2022") +
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold"),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank())

#------------------2023 Top-5 municipalities ------------------

plot_4 <- aggregated_data_2023_t %>%
  ggplot(aes(x = reorder(municipality, -total), 
             y = total)) +
  geom_bar(stat = "identity", 
           fill = "#556B2F") + 
  geom_text(aes(label = total), 
            vjust = -0.3, 
            size = 2.5) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 14000, by = 1000)) +
  labs(x = "Municipality", 
       y = "Total Number of Newcomers", 
       title = "Top 5 Municipalities by Newcomers, 2023") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank())

# Saving the plots:
#ggsave("../plots/top5_2020.jpg", plot = plot_1)
#ggsave("../plots/top5_2021.jpg", plot = plot_2)
#ggsave("../plots/top5_2022.jpg", plot = plot_3)
#ggsave("../plots/top5_2023.jpg", plot = plot_4)
```

## Joining statistical data with spatial data:

```{r}
data_2020 <- mun %>% dplyr::inner_join(aggregated_data_2020, by = c("NAME_2"="municipality"))
data_2021 <- mun %>% dplyr::inner_join(aggregated_data_2021, by = c("NAME_2"="municipality"))
data_2022 <- mun %>% dplyr::inner_join(aggregated_data_2022, by = c("NAME_2"="municipality"))
data_2023 <- mun %>% dplyr::inner_join(aggregated_data_2023, by = c("NAME_2"="municipality"))
```


## MAP for 2020:

1. Adding extra columns to the data for labels:

```{r}
data_2020$NAME_3 <- ifelse(data_2020$total == 2067, as.character(data_2020$NAME_2), NA) # Odense
data_2020$NAME_4 <- ifelse(data_2020$total == 3856, as.character(data_2020$NAME_2), NA) # Aarhus
data_2020$NAME_5 <- ifelse(data_2020$total == 12891, as.character(data_2020$NAME_2), NA) # Copenhagen
data_2020$NAME_6 <- ifelse(data_2020$total == 2066, as.character(data_2020$NAME_2), NA) # Frederiksberg
data_2020$NAME_7 <- ifelse(data_2020$total == 1880, as.character(data_2020$NAME_2), NA) # Aalborg
```

2. Creating small map-snippet for the main plot:

```{r}
cph_fred_2020 <- data_2020 %>% 
  filter(NAME_2 == "Copenhagen" | NAME_2 == "Frederiksberg")

tmap_mode("plot")

tm_2020_snippet <- tm_shape(cph_fred_2020) +
  tm_borders() +
  tm_layout(frame = TRUE, frame.lwd = 1.5,
            legend.show = FALSE,
            asp = 1.2) + 
  tm_fill(col = "total",
          style = "fixed", breaks = c(10, 120, 200, 300, 500, 1000, 4000, 12891)) +
  tm_shape(cph_fred_2020) +
  tm_text("NAME_5", size = 0.5, col = "black", fontface = "bold", xmod = -1.5, ymod = -2.5) +
  tm_shape(cph_fred_2020) +
  tm_text("NAME_6", size = 0.5, col = "black", fontface = "bold")
  
#tm_2020_snippet
```

3. Creating Copenhagen's bounding box (this one will be used for further maps as well):

```{r}
cph <- data_2020 %>%
  subset(NAME_2 == "Copenhagen")

bbox <- st_make_grid(cph$geometry, n = 1)
```

4. Plotting everything in one for 2020:

```{r}
tmap_mode("plot")

tm_2020 <- tm_shape(data_2020) +
  tm_fill(col = "total", title = "Total number \nof Newcomers", 
          style = "fixed", breaks = c(10, 120, 200, 300, 500, 1000, 4000, 12891))+
  tm_borders() +
  tm_layout(main.title = "Total number of Newcomers across municipalities, 2020", 
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold",
            asp = 1.5, frame = FALSE) +
  tm_compass(north = 0, size = 1.5, position = c("LEFT", "bottom")) +
  tm_scale_bar(position = c("LEFT", "bottom")) + 
  tm_credits(text = "Data source: Statistics Denmark, www.dst.dk", position = c("RIGHT", "bottom"), size = 0.5) +
  #tm_legend(position=c("left", "top")) +
  tm_shape(data_2020 %>% top_n(5, total)) +
  tm_borders(col = "black", lwd = 1.2) + 
  tm_text("NAME_3", size = 0.7, col = "black", xmod = 1.6, ymod = 0.5, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.4) + # Odense label
  tm_shape(data_2020) +
  tm_text("NAME_4", size = 0.7, col = "black", xmod = 1.5, ymod = -0.6, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Aarhus label
  tm_shape(data_2020) +
  tm_text("NAME_5", size = 0.7, col = "black", xmod = 1, ymod = -0.7, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Copenhagen label
  tm_shape(data_2020) +
  tm_text("NAME_6", size = 0.7, col = "black", xmod = 2.3, ymod = 0.4, fontface = "bold") + # Frederiksberg label
  tm_shape(data_2020) +
  tm_text("NAME_7", size = 0.7, col = "black", xmod = 2.4, ymod = 0, fontface = "bold") +  # Aalborg label
  tm_shape(bbox) + tm_borders(col = "black") # Bounding box object
#tm_2020
```

5. Plotting the main map and saving it:

```{r}
main_map_2020 <- tmap_grob(tm_2020) 
snippet_map_2020 <- tmap_grob(tm_2020_snippet) 

map_2020 <- ggdraw() +
  draw_plot(main_map_2020) +
  draw_plot(snippet_map_2020,
    height = 0.3,
    x = 0.34,
    y = 0.26,
    scale = 0.8
  )

#map_2020
ggsave("../plots/Denmark_Newcomers_2020.png", map_2020, width = 7, height = 5, dpi = 400, units = "in")
```

## MAP for 2021:

1. Adding extra columns to the data for labels:

```{r}
data_2021$NAME_3 <- ifelse(data_2021$total == 2378, as.character(data_2021$NAME_2), NA) # Odense
data_2021$NAME_4 <- ifelse(data_2021$total == 4118, as.character(data_2021$NAME_2), NA) # Aarhus
data_2021$NAME_5 <- ifelse(data_2021$total == 14267, as.character(data_2021$NAME_2), NA) # Copenhagen
data_2021$NAME_6 <- ifelse(data_2021$total == 2071, as.character(data_2021$NAME_2), NA) # Frederiksberg
data_2021$NAME_7 <- ifelse(data_2021$total == 1948, as.character(data_2021$NAME_2), NA) # Aalborg
```

2. Creating small map-snippet for the main plot:

```{r}
cph_fred_2021 <- data_2021 %>% 
  filter(NAME_2 == "Copenhagen" | NAME_2 == "Frederiksberg")

tmap_mode("plot")

tm_2021_snippet <- tm_shape(cph_fred_2021) +
  tm_borders() +
  tm_layout(frame = TRUE, frame.lwd = 1.5,
            legend.show = FALSE,
            asp = 1.2) + 
  tm_fill(col = "total",
          style = "fixed", breaks = c(2, 160, 250, 350, 650, 1900, 4200, 14267)) +
  tm_shape(cph_fred_2021) +
  tm_text("NAME_5", size = 0.5, col = "black", fontface = "bold", xmod = -1.5, ymod = -2.5) +
  tm_shape(cph_fred_2021) +
  tm_text("NAME_6", size = 0.5, col = "black", fontface = "bold")
  
#tm_2021_snippet
```

3. Plotting everything in one for 2021:

```{r}
tmap_mode("plot")

tm_2021 <- tm_shape(data_2021) +
  tm_fill(col = "total", title = "Total number \nof Newcomers", 
          style = "fixed", breaks = c(2, 160, 250, 350, 650, 1900, 4200, 14267)) +
  tm_borders() +
  tm_layout(main.title = "Total number of Newcomers across municipalities, 2021", 
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold",
            asp = 1.5, frame = FALSE) +
  tm_compass(north = 0, size = 1.5, position = c("LEFT", "bottom")) +
  tm_scale_bar(position = c("LEFT", "bottom")) + 
  tm_credits(text = "Data source: Statistics Denmark, www.dst.dk", position = c("RIGHT", "bottom"), size = 0.5) +
  #tm_legend(position=c("left", "top")) +
  tm_shape(data_2021 %>% top_n(5, total)) +
  tm_borders(col = "black", lwd = 1.2) + 
  tm_text("NAME_3", size = 0.7, col = "black", xmod = 1.6, ymod = 0.5, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.4) + # Odense label
  tm_shape(data_2021) +
  tm_text("NAME_4", size = 0.7, col = "black", xmod = 1.5, ymod = -0.6, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Aarhus label
  tm_shape(data_2021) +
  tm_text("NAME_5", size = 0.7, col = "black", xmod = 1, ymod = -0.7, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Copenhagen label
  tm_shape(data_2021) +
  tm_text("NAME_6", size = 0.7, col = "black", xmod = 2.3, ymod = 0.4, fontface = "bold") + # Frederiksberg label
  tm_shape(data_2021) +
  tm_text("NAME_7", size = 0.7, col = "black", xmod = 2.4, ymod = 0, fontface = "bold") +  # Aalborg label
  tm_shape(bbox) + tm_borders(col = "black")

#tm_2021
```

4. Plotting the main map and saving it:

```{r}
main_map_2021 <- tmap_grob(tm_2021) 
snippet_map_2021 <- tmap_grob(tm_2021_snippet) 

map_2021 <- ggdraw() +
  draw_plot(main_map_2021) +
  draw_plot(snippet_map_2021,
    height = 0.3,
    x = 0.34,
    y = 0.26,
    scale = 0.8
  )

#map_2021
ggsave("../plots/Denmark_Newcomers_2021.png", map_2021, width = 7, height = 5, dpi = 400, units = "in")
```

## MAP for 2022:

1. Adding extra columns to the data for labels:

```{r}
data_2022$NAME_3 <- ifelse(data_2022$total == 3776, as.character(data_2022$NAME_2), NA) # Odense
data_2022$NAME_4 <- ifelse(data_2022$total == 7142, as.character(data_2022$NAME_2), NA) # Aarhus
data_2022$NAME_5 <- ifelse(data_2022$total == 21940, as.character(data_2022$NAME_2), NA) # Copenhagen
data_2022$NAME_6 <- ifelse(data_2022$total == 3288, as.character(data_2022$NAME_2), NA) # Frederiksberg
data_2022$NAME_7 <- ifelse(data_2022$total == 3231, as.character(data_2022$NAME_2), NA) # Aalborg
```

2. Creating small map-snippet for the main plot:

```{r}
cph_fred_2022 <- data_2022 %>% 
  filter(NAME_2 == "Copenhagen" | NAME_2 == "Frederiksberg")

tmap_mode("plot")

tm_2022_snippet <- tm_shape(cph_fred_2022) +
  tm_borders() +
  tm_layout(frame = TRUE, frame.lwd = 1.5,
            legend.show = FALSE,
            asp = 1.2) + 
  tm_fill(col = "total",
          style = "fixed", breaks = c(13, 400, 500, 710, 1500, 3200, 7200, 21940)) +
  tm_shape(cph_fred_2022) +
  tm_text("NAME_5", size = 0.5, col = "black", fontface = "bold", xmod = -1.5, ymod = -2.5) +
  tm_shape(cph_fred_2022) +
  tm_text("NAME_6", size = 0.5, col = "black", fontface = "bold")
  
#tm_2022_snippet
```

3. Plotting everything in one for 2022:

```{r}
tmap_mode("plot")

tm_2022 <- tm_shape(data_2022) +
  tm_fill(col = "total", title = "Total number \nof Newcomers", 
          style = "fixed", breaks = c(13, 400, 500, 710, 1500, 3200, 7200, 21940)) +
  tm_borders() +
  tm_layout(main.title = "Total number of Newcomers across municipalities, 2022", 
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold",
            asp = 1.5, frame = FALSE) +
  tm_compass(north = 0, size = 1.5, position = c("LEFT", "bottom")) +
  tm_scale_bar(position = c("LEFT", "bottom")) + 
  tm_credits(text = "Data source: Statistics Denmark, www.dst.dk", position = c("RIGHT", "bottom"), size = 0.5) +
  #tm_legend(position=c("left", "top")) +
  tm_shape(data_2022 %>% top_n(5, total)) +
  tm_borders(col = "black", lwd = 1.2) + 
  tm_text("NAME_3", size = 0.7, col = "black", xmod = 1.6, ymod = 0.5, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.4) + # Odense label
  tm_shape(data_2022) +
  tm_text("NAME_4", size = 0.7, col = "black", xmod = 1.5, ymod = -0.6, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Aarhus label
  tm_shape(data_2022) +
  tm_text("NAME_5", size = 0.7, col = "black", xmod = 1, ymod = -0.7, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Copenhagen label
  tm_shape(data_2022) +
  tm_text("NAME_6", size = 0.7, col = "black", xmod = 2.3, ymod = 0.4, fontface = "bold") + # Frederiksberg label
  tm_shape(data_2022) +
  tm_text("NAME_7", size = 0.7, col = "black", xmod = 2.4, ymod = 0, fontface = "bold") +  # Aalborg label
  tm_shape(bbox) + tm_borders(col = "black")
#tm_2022
```

4. Plotting the main map and saving it:

```{r}
main_map_2022 <- tmap_grob(tm_2022) 
snippet_map_2022 <- tmap_grob(tm_2022_snippet) 

map_2022 <- ggdraw() +
  draw_plot(main_map_2022) +
  draw_plot(snippet_map_2022,
    height = 0.3,
    x = 0.34,
    y = 0.26,
    scale = 0.8
  )

#map_2022
ggsave("../plots/Denmark_Newcomers_2022.png", map_2022, width = 7, height = 5, dpi = 400, units = "in")
```


## MAP for 2023:

1. Adding extra columns to the data for labels:

```{r}
data_2023$NAME_3 <- ifelse(data_2023$total == 2881, as.character(data_2023$NAME_2), NA) # Odense
data_2023$NAME_4 <- ifelse(data_2023$total == 6037, as.character(data_2023$NAME_2), NA) # Aarhus
data_2023$NAME_5 <- ifelse(data_2023$total == 20243, as.character(data_2023$NAME_2), NA) # Copenhagen
data_2023$NAME_6 <- ifelse(data_2023$total == 2889, as.character(data_2023$NAME_2), NA) # Frederiksberg
data_2023$NAME_7 <- ifelse(data_2023$total == 2069, as.character(data_2023$NAME_2), NA) # Aalborg
```

2. Creating small map-snippet for the main plot:

```{r}
cph_fred_2023 <- data_2023 %>% 
  filter(NAME_2 == "Copenhagen" | NAME_2 == "Frederiksberg")

tmap_mode("plot")

tm_2023_snippet <- tm_shape(cph_fred_2023) +
  tm_borders() +
  tm_layout(frame = TRUE, frame.lwd = 1.5,
            legend.show = FALSE,
            asp = 1.2) + 
  tm_fill(col = "total",
          style = "fixed", breaks = c(13, 210, 370, 520, 840, 2000, 6100, 20243)) +
  tm_shape(cph_fred_2023) +
  tm_text("NAME_5", size = 0.5, col = "black", fontface = "bold", xmod = -1.5, ymod = -2.5) +
  tm_shape(cph_fred_2023) +
  tm_text("NAME_6", size = 0.5, col = "black", fontface = "bold")
  
#tm_2023_snippet
```

3. Plotting everything in one for 2023:

```{r}
tmap_mode("plot")

tm_2023 <- tm_shape(data_2023) +
  tm_fill(col = "total", title = "Total number \nof Newcomers", 
          style = "fixed", breaks = c(13, 210, 370, 520, 840, 2000, 6100, 20243)) +
  tm_borders() +
  tm_layout(main.title = "Total number of Newcomers across municipalities, 2023", 
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold",
            asp = 1.5, frame = FALSE) +
  tm_compass(north = 0, size = 1.5, position = c("LEFT", "bottom")) +
  tm_scale_bar(position = c("LEFT", "bottom")) + 
  tm_credits(text = "Data source: Statistics Denmark, www.dst.dk", position = c("RIGHT", "bottom"), size = 0.5) +
  #tm_legend(position=c("left", "top")) +
  tm_shape(data_2023 %>% top_n(5, total)) +
  tm_borders(col = "black", lwd = 1.2) + 
  tm_text("NAME_3", size = 0.7, col = "black", xmod = 1.6, ymod = 0.5, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.4) + # Odense label
  tm_shape(data_2023) +
  tm_text("NAME_4", size = 0.7, col = "black", xmod = 1.5, ymod = -0.6, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Aarhus label
  tm_shape(data_2023) +
  tm_text("NAME_5", size = 0.7, col = "black", xmod = 1, ymod = -0.7, 
          fontface = "bold", bg.color = "white", bg.alpha = 0.3) + # Copenhagen label
  tm_shape(data_2023) +
  tm_text("NAME_6", size = 0.7, col = "black", xmod = 2.3, ymod = 0.4, fontface = "bold") + # Frederiksberg label
  tm_shape(data_2023) +
  tm_text("NAME_7", size = 0.7, col = "black", xmod = 2.4, ymod = 0, fontface = "bold") +  # Aalborg label
  tm_shape(bbox) + tm_borders(col = "black")
#tm_2023
```

4. Plotting the main map and saving it:

```{r}
main_map_2023 <- tmap_grob(tm_2023) 
snippet_map_2023 <- tmap_grob(tm_2023_snippet) 

map_2023 <- ggdraw() +
  draw_plot(main_map_2023) +
  draw_plot(snippet_map_2023,
    height = 0.3,
    x = 0.34,
    y = 0.26,
    scale = 0.8
  )

#map_2023
ggsave("../plots/Denmark_Newcomers_2023.png", map_2023, width = 7, height = 5, dpi = 400, units = "in")
```

## Creating cartograms for 4 datasets:

Create plots:

```{r}
cart_plot_2020 <- cartogram_cont(data_2020, "total")
cart_plot_2021 <- cartogram_cont(data_2021, "total")
cart_plot_2022 <- cartogram_cont(data_2022, "total")
cart_plot_2023 <- cartogram_cont(data_2023, "total")
```

Save plots:

```{r}
png("../plots/cartogram_2020.png", width = 800, height = 600)
plot(cart_plot_2020$geometry,
     main = "Cartogram of total number \nof Newcomers across municipalities, 2020")
dev.off()  # Close the device

png("../plots/cartogram_2021.png", width = 800, height = 600)
plot(cart_plot_2021$geometry,
     main = "Cartogram of total number \nof Newcomers across municipalities, 2021")
dev.off()  # Close the device

png("../plots/cartogram_2022.png", width = 800, height = 600)
plot(cart_plot_2022$geometry,
     main = "Cartogram of total number \nof Newcomers across municipalities, 2022")
dev.off()  # Close the device

png("../plots/cartogram_2023.png", width = 800, height = 600)
plot(cart_plot_2023$geometry,
     main = "Cartogram of total number \nof Newcomers across municipalities, 2023")
dev.off()  # Close the device
```


## Calculating the percentage of people that came from America, Europe, Africa, Oceania and Asia regions.

```{r}
americas <- c("USA", "Brazil", "Mexico", "Colombia", "Argentina", "Canada", "Peru", "Venezuela",
              "Chile", "Ecuador", "Guatemala", "Bolivia", "Haiti", "Cuba", "Dominican Republic", "Honduras",
              "Paraguay", "El Salvador", "Nicaragua", "Costa Rica", "Panama", "Uruguay", "Jamaica", 
              "Trinidad and Tobago", "Guyana", "Suriname", "Belize", "Bahamas", "Barbados", "Saint Lucia",
              "Grenada", "Saint Vincent and the Grenadines", "Antigua and Barbuda", "Dominica", 
              "Dominican Republic", "Saint Kitts and Nevis", "Guyana")

europe <- c("Austria", "Albania", "Belgium", "Belarus", "Bulgaria", "Bosnia and Herzegovina",  
            "Croatia", "Cyprus", "Czech Republic", 
            "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", 
            "Ireland", "Italy", "Latvia", "Lithuania", "Luxembourg", "Malta", "Netherlands", 
            "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", "Sweden", "Iceland", "Kosovo",
            "Moldova", "Montenegro", "Macedonia", "Norway", "Serbia", "Serbia and Montenegro", "Switzerland",
            "Ukraine", "United Kingdom", "Andorra", "Liechtenstein", "Andorra")

africa <- c(
  "Algeria", "Angola", "Benin", "Botswana", "Burkina Faso", "Burundi", "Cabo Verde", "Cameroon", 
  "Central African Republic", "Chad", "Comoros", "Congo, Democratic Republic of the", 
  "Congo", "Djibouti", "Egypt", "Equatorial Guinea", "Eritrea", "Eswatini", "Ethiopia", "Gabon", 
  "Gambia", "Ghana", "Guinea", "Guinea-Bissau", "Ivory Coast", "Kenya",
  "Lesotho", "Liberia", "Libya", "Madagascar", "Malawi", "Mali", "Mauritania", "Mauritius", 
  "Morocco", "Mozambique", "Namibia", "Niger", "Nigeria", "Rwanda", "Sao Tome and Principe", 
  "Senegal", "Seychelles", "Sierra Leone", "Somalia", "South Africa", "South Sudan", "Sudan", 
  "Tanzania", "Togo", "Tunisia", "Uganda", "Zambia", "Zimbabwe", "Eswantini", "Cape Verde")

asia <- c(
  "Afghanistan", "Armenia", "Azerbaijan", "Bahrain", "Bangladesh", "Bhutan", "Brunei", "Cambodia", 
  "China", "Cyprus", "Georgia", "India", "Indonesia", "Iran", "Iraq", "Israel", "Japan", "Jordan", 
  "Kazakhstan", "Kuwait", "Kyrgyzstan", "Laos", "Lebanon", "Malaysia", "Maldives", "Mongolia", 
  "Myanmar (Burma)", "Nepal", "North Korea", "Oman", "Pakistan", "Palestine", "Philippines", 
  "Qatar", "Saudi Arabia", "Singapore", "South Korea", "Sri Lanka", "Syria", "Taiwan", "Tajikistan", 
  "Thailand", "Timor-Leste (East Timor)", "Turkey", "Turkmenistan", "United Arab Emirates", "Uzbekistan", 
  "Vietnam", "Yemen", "Myanmar", "Russia", "Brunei", "Myanmar (Burma)", "Myanmar", "Burma", "Oman", "Palestine",
  "Timor-Leste", "United Arab Emirates")

oceania <- c("Australia", "Fiji", "New Zealand", "Samoa", "Tonga", "Nauru","Vanuatu")
```


Calculating the percentage of people coming from each region to Denmark:

```{r}
df_20 <- df %>%
  filter(year == 2020)

df_21 <- df %>%
  filter(year == 2021)

df_22 <- df %>%
  filter(year == 2022)

df_23 <- df %>%
  filter(year == 2023)

# ----------2020----------

continent <- c()

for (org in df_20$origin) {
  if (org %in% americas) {
    continent <- c(continent, "America")
  } else if (org %in% europe) {
    continent <- c(continent, "Europe")
  } else if (org %in% africa) {
    continent <- c(continent, "Africa")
  } else if (org %in% asia) {
    continent <- c(continent, "Asia")
  } else if (org %in% oceania) {
    continent <- c(continent, "Oceania")
  }
}

df_20$continent <- continent

# ----------2021----------

continent_1 <- c()

for (org in df_21$origin) {
  if (org %in% americas) {
    continent_1 <- c(continent_1, "America")
  } else if (org %in% europe) {
    continent_1 <- c(continent_1, "Europe")
  } else if (org %in% africa) {
    continent_1 <- c(continent_1, "Africa")
  } else if (org %in% asia) {
    continent_1 <- c(continent_1, "Asia")
  } else if (org %in% oceania) {
    continent_1 <- c(continent_1, "Oceania")
  }
}
df_21$continent <- continent_1

# ----------2022----------

continent_2 <- c()

for (org in df_22$origin) {
  if (org %in% americas) {
    continent_2 <- c(continent_2, "America")
  } else if (org %in% europe) {
    continent_2 <- c(continent_2, "Europe")
  } else if (org %in% africa) {
    continent_2 <- c(continent_2, "Africa")
  } else if (org %in% asia) {
    continent_2 <- c(continent_2, "Asia")
  } else if (org %in% oceania) {
    continent_2 <- c(continent_2, "Oceania")
  }
}
df_22$continent <- continent_2

# ----------2023----------

continent_3 <- c()

for (org in df_23$origin) {
  if (org %in% americas) {
    continent_3 <- c(continent_3, "America")
  } else if (org %in% europe) {
    continent_3 <- c(continent_3, "Europe")
  } else if (org %in% africa) {
    continent_3 <- c(continent_3, "Africa")
  } else if (org %in% asia) {
    continent_3 <- c(continent_3, "Asia")
  } else if (org %in% oceania) {
    continent_3 <- c(continent_3, "Oceania")
  }
}

df_23$continent <- continent_3
```


### The code below calculates the percentage of newcomers in Denmark by the "region" of origin.

```{r}
# ----------Calculating the sum of newcomers per each year----------

n_foreigners_2020 <- sum(df_20$n)
n_foreigners_2021 <- sum(df_21$n) 
n_foreigners_2022 <- sum(df_22$n) 
n_foreigners_2023 <- sum(df_23$n) 


# ----------2020----------

continent_data_2020 <- df_20 %>%
  group_by(continent) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))

pct_2020 <- c()

for (num in continent_data_2020$total) {
  percentage <- round(num*100/n_foreigners_2020, 1)
  pct_2020 <- c(pct_2020, percentage)
}

continent_data_2020$pct <- pct_2020
continent_data_2020$year <- 2020


# ----------2021----------

continent_data_2021 <- df_21 %>%
  group_by(continent) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))

pct_2021 <- c()

for (num in continent_data_2021$total) {
  percentage <- round(num*100/n_foreigners_2021, 1)
  pct_2021 <- c(pct_2021, percentage)
}

continent_data_2021$pct <- pct_2021
continent_data_2021$year <- 2021

# ----------2022----------

continent_data_2022 <- df_22 %>%
  group_by(continent) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))

pct_2022 <- c()

for (num in continent_data_2022$total) {
  percentage <- round(num*100/n_foreigners_2022, 1)
  pct_2022 <- c(pct_2022, percentage)
}

continent_data_2022$pct <- pct_2022
continent_data_2022$year <- 2022

# ----------2023----------

continent_data_2023 <- df_23 %>%
  group_by(continent) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total))

pct_2023 <- c()

for (num in continent_data_2023$total) {
  percentage <- round(num*100/n_foreigners_2023, 1)
  pct_2023 <- c(pct_2023, percentage)
}

continent_data_2023$pct <- pct_2023
continent_data_2023$year <- 2023

# ----------Combine all data together, save it as an image for Appendix----------

grand_continent_data <- rbind(continent_data_2020, continent_data_2021, continent_data_2022, continent_data_2023)

# Change the column names:
colnames(grand_continent_data) <- c("Region", "Total", "Percentage", "Year")

data_table_1 <- kable(grand_continent_data, format = "html", table.attr = "style='width:100%;'") %>%
  kable_styling(full_width = F, position = "center", bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(0, bold = TRUE, color = "white", background = "black") %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

save_kable(data_table_1, "../plots/data_table_1.png")

# Visualising

palette <- c("#8B4513","#556B2F", "#A0522D", "#CD853F", "#D2B48C")

plot_cont_d <- grand_continent_data %>%
  ggplot(aes(x = Region, y = Percentage, fill = Region)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = Percentage), vjust = -0.3, size = 2.5) +
  theme_minimal() +
  facet_wrap(~Year, scales = "free_x") +
  scale_fill_manual(values = palette) +  # Corrected scale_fill_manual
  scale_y_continuous(breaks = seq(0, 14000, by = 1000)) +
  labs(x = "Region", y = "Percentage of Newcomers", title = "Percentage of Newcomers across regions, 2020-2023") +
  theme(
        plot.title = element_text(hjust = 0.5, face = "bold"),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = "none")

#ggsave("../plots/per_continent.jpg", plot = plot_cont_d)

# The code below is used to calculate the average percentages - this is used in the paper:
europe_d <- filter(grand_continent_data, Region == "Europe")
mean(europe_d$Percentage)

asia_d <- filter(grand_continent_data, Region == "Asia")
mean(asia_d$Percentage)

africa_d <- filter(grand_continent_data, Region == "Africa")
mean(africa_d$Percentage)

oceania_d <- filter(grand_continent_data, Region == "Oceania")
mean(oceania_d$Percentage)

america_d <- filter(grand_continent_data, Region == "America")
mean(america_d$Percentage)
```

### Finding the origins to run the analysis for (according to the number of newcomers):

```{r}
df_with_continents <- df

origin_by_municipality <- df_with_continents %>%
  group_by(origin) %>%
  summarise(origin_total = sum(n))

continent_4 <- c()

for (org in origin_by_municipality$origin) {
  if (org %in% americas) {
    continent_4 <- c(continent_4, "America")
  } else if (org %in% europe) {
    continent_4 <- c(continent_4, "Europe")
  } else if (org %in% africa) {
    continent_4 <- c(continent_4, "Africa")
  } else if (org %in% asia) {
    continent_4 <- c(continent_4, "Asia")
  } else if (org %in% oceania) {
    continent_4 <- c(continent_4, "Oceania")
  }
}

origin_by_municipality$continent <- continent_4

# ----------See from where migration happens the most - data to use for the analysis----------

# Since over 70%, generally, migrants come from Europe, I will look into 4 countries from Europe. For other regions, I am analysing only the top 1 (except Asia - top 2).

top_4_europe <- origin_by_municipality %>%
  filter(continent == "Europe") %>%
  arrange(desc(origin_total)) %>%
  head(4)

top_1_america <- origin_by_municipality %>%
  filter(continent == "America") %>%
  arrange(desc(origin_total)) %>%
  head(1)

top_2_asia <- origin_by_municipality %>%
  filter(continent == "Asia") %>%
  arrange(desc(origin_total)) %>%
  head(2)

top_1_africa <- origin_by_municipality %>%
  filter(continent == "Africa") %>%
  arrange(desc(origin_total)) %>%
  head(1)

top_1_oceania <- origin_by_municipality %>%
  filter(continent == "Oceania") %>%
  arrange(desc(origin_total)) %>%
  head(1)

top_per_continent <- rbind(top_4_europe, top_2_asia, top_1_america,
                                  top_1_africa, top_1_oceania)
```


## Create data frame for analysis:

```{r}
spatial_data <- mun %>% dplyr::inner_join(df, by = c("NAME_2"="municipality"))
```

## Performing Morans I test with Monte Carlo simulations

### People coming from Ukraine:

```{r}
ukraine <- df %>%
  filter(origin == "Ukraine") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

ukraine <- mun %>% dplyr::inner_join(ukraine, by = c("NAME_2"="municipality"))

ukraine_map <- tm_shape(ukraine) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Ukraine, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
#tmap_save(ukraine_map, "../plots/Ukraine.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
ukraine_queen_nb <- poly2nb(ukraine$geometry, queen = TRUE)
ukraine_centers <- st_coordinates(st_centroid(ukraine$geometry))

# Saving the plot:
png("../plots/ukraine_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(ukraine_queen_nb, ukraine_centers, col = "red",add = TRUE)
title("Queen Contiguity, Ukraine")
dev.off()

# Test:
moran.mc(ukraine$origin_total, 
         nb2listw(ukraine_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
ukraine_centers_2 <- st_centroid(ukraine$geometry, of_largest_polygon = TRUE)
ukraine_nb_25km <- dnearneigh(ukraine_centers_2, 0, 25000)

# Saving the plot:
png("../plots/ukraine_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(ukraine_nb_25km, ukraine_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Ukraine")
dev.off()

# Test:
moran.mc(ukraine$origin_total, 
         nb2listw(ukraine_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
ukraine_nb_50km <- dnearneigh(ukraine_centers_2, 0, 50000)

# Saving the plot:
png("../plots/ukraine_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(ukraine_nb_50km, ukraine_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Ukraine")
dev.off()

# Test:
moran.mc(ukraine$origin_total, 
         nb2listw(ukraine_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
ukraine_nb_k3 <- knearneigh(ukraine_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(ukraine, "Spatial"))
ukraine_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/ukraine_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(ukraine_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Ukraine")
dev.off()

# Test:
moran.mc(ukraine$origin_total,
         nb2listw(knn2nb(ukraine_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from Romania:

```{r}
romania <- df %>%
  filter(origin == "Romania") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

romania <- mun %>% dplyr::inner_join(romania, by = c("NAME_2"="municipality"))

romania_map <- tm_shape(romania) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Romania, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
tmap_save(romania_map, "../plots/Romania.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
romania_queen_nb <- poly2nb(romania$geometry, queen = TRUE)
romania_centers <- st_coordinates(st_centroid(romania$geometry))

# Saving the plot:
png("../plots/romania_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(romania_queen_nb, romania_centers, col = "red",add = TRUE)
title("Queen Contiguity, Romania")
dev.off()


# Test:
moran.mc(romania$origin_total, 
         nb2listw(romania_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
romania_centers_2 <- st_centroid(romania$geometry, of_largest_polygon = TRUE)
romania_nb_25km <- dnearneigh(romania_centers_2, 0, 25000)

# Saving the plot:
png("../plots/romania_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(romania_nb_25km, romania_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Romania")
dev.off()


# Test:
moran.mc(romania$origin_total, 
         nb2listw(romania_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
romania_nb_50km <- dnearneigh(romania_centers_2, 0, 50000)

# Saving the plot:
png("../plots/romania_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(romania_nb_50km, romania_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Romania")
dev.off()


# Test:
moran.mc(romania$origin_total, 
         nb2listw(romania_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
romania_nb_k3 <- knearneigh(romania_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(romania, "Spatial"))
romania_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/romania_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(romania_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Romania")
dev.off()

# Test:
moran.mc(romania$origin_total,
         nb2listw(knn2nb(romania_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from Germany:

```{r}
germany <- df %>%
  filter(origin == "Germany") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

germany <- mun %>% dplyr::inner_join(germany, by = c("NAME_2"="municipality"))

germany_map <- tm_shape(germany) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Germany, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(germany_map, "../plots/Germany.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
germany_queen_nb <- poly2nb(germany$geometry, queen = TRUE)
germany_centers <- st_coordinates(st_centroid(germany$geometry))

# Saving the plot:
png("../plots/germany_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(germany_queen_nb, germany_centers, col = "red",add = TRUE)
title("Queen Contiguity, Germany")
dev.off()

# Test:
moran.mc(germany$origin_total, 
         nb2listw(germany_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
germany_centers_2 <- st_centroid(germany$geometry, of_largest_polygon = TRUE)
germany_nb_25km <- dnearneigh(germany_centers_2, 0, 25000)

# Saving the plot:
png("../plots/germany_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(germany_nb_25km, germany_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Germany")
dev.off()


# Test:
moran.mc(germany$origin_total, 
         nb2listw(germany_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
germany_nb_50km <- dnearneigh(germany_centers_2, 0, 50000)

# Saving the plot:
png("../plots/germany_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(germany_nb_50km, germany_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Germany")
dev.off()

# Test:
moran.mc(germany$origin_total, 
         nb2listw(germany_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
germany_nb_k3 <- knearneigh(germany_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(germany, "Spatial"))
germany_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/germany_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(germany_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Germany")
dev.off()


# Test:
moran.mc(germany$origin_total,
         nb2listw(knn2nb(germany_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from India:

```{r}
india <- df %>%
  filter(origin == "India") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

india <- mun %>% dplyr::inner_join(india, by = c("NAME_2"="municipality"))

india_map <- tm_shape(india) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from India, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(india_map, "../plots/India.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
india_queen_nb <- poly2nb(india$geometry, queen = TRUE)
india_centers <- st_coordinates(st_centroid(india$geometry))

# Saving the plot:
png("../plots/india_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(india_queen_nb, india_centers, col = "red",add = TRUE)
title("Queen Contiguity, India")
dev.off()


# Test:
moran.mc(india$origin_total, 
         nb2listw(india_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
india_centers_2 <- st_centroid(india$geometry, of_largest_polygon = TRUE)
india_nb_25km <- dnearneigh(india_centers_2, 0, 25000)

# Saving the plot:
png("../plots/india_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(india_nb_25km, india_centers_2, col = "red",add = TRUE)
title("Distance of 25km, India")
dev.off()


# Test:
moran.mc(india$origin_total, 
         nb2listw(india_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
india_nb_50km <- dnearneigh(india_centers_2, 0, 50000)

# Saving the plot:
png("../plots/india_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(india_nb_50km, india_centers_2, col = "red",add = TRUE)
title("Distance of 50km, India")
dev.off()


# Test:
moran.mc(india$origin_total, 
         nb2listw(india_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
india_nb_k3 <- knearneigh(india_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(india, "Spatial"))
india_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/india_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(india_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), India")
dev.off()


# Test:
moran.mc(india$origin_total,
         nb2listw(knn2nb(india_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from China:

```{r}
china <- df %>%
  filter(origin == "China") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

china <- mun %>% dplyr::inner_join(china, by = c("NAME_2"="municipality"))

china_map <- tm_shape(ukraine) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from China, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(china_map, "../plots/China.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
china_queen_nb <- poly2nb(china$geometry, queen = TRUE)
china_centers <- st_coordinates(st_centroid(china$geometry))

# Saving the plot:
png("../plots/china_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(china_queen_nb, china_centers, col = "red",add = TRUE)
title("Queen Contiguity, China")
dev.off()

# Test:
moran.mc(china$origin_total, 
         nb2listw(china_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
china_centers_2 <- st_centroid(china$geometry, of_largest_polygon = TRUE)
china_nb_25km <- dnearneigh(china_centers_2, 0, 25000)

# Saving the plot:
png("../plots/china_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(china_nb_25km, china_centers_2, col = "red",add = TRUE)
title("Distance of 25km, China")
dev.off()

# Test:
moran.mc(china$origin_total, 
         nb2listw(china_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
china_nb_50km <- dnearneigh(china_centers_2, 0, 50000)

# Saving the plot:
png("../plots/china_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(china_nb_50km, china_centers_2, col = "red",add = TRUE)
title("Distance of 50km, China")
dev.off()

# Test:
moran.mc(china$origin_total, 
         nb2listw(china_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
china_nb_k3 <- knearneigh(china_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(china, "Spatial"))
china_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/china_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(china_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), China")
dev.off()


# Test:
moran.mc(china$origin_total,
         nb2listw(knn2nb(china_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from USA:

```{r}
usa <- df %>%
  filter(origin == "USA") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

usa <- mun %>% dplyr::inner_join(usa, by = c("NAME_2"="municipality"))

usa_map <- tm_shape(ukraine) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from USA, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(usa_map, "../plots/USA.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
usa_queen_nb <- poly2nb(usa$geometry, queen = TRUE)
usa_centers <- st_coordinates(st_centroid(usa$geometry))

# Saving the plot:
png("../plots/usa_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(usa_queen_nb,usa_centers, col = "red",add = TRUE)
title("Queen Contiguity, USA")
dev.off()


# Test:
moran.mc(usa$origin_total, 
         nb2listw(usa_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
usa_centers_2 <- st_centroid(usa$geometry, of_largest_polygon = TRUE)
usa_nb_25km <- dnearneigh(usa_centers_2, 0, 25000)

# Saving the plot:
png("../plots/usa_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(usa_nb_25km, usa_centers_2, col = "red",add = TRUE)
title("Distance of 25km, USA")
dev.off()

# Test:
moran.mc(usa$origin_total, 
         nb2listw(usa_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
usa_nb_50km <- dnearneigh(usa_centers_2, 0, 50000)

# Saving the plot:
png("../plots/usa_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(usa_nb_50km, usa_centers_2, col = "red",add = TRUE)
title("Distance of 50km, USA")
dev.off()


# Test:
moran.mc(usa$origin_total, 
         nb2listw(usa_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
usa_nb_k3 <- knearneigh(usa_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(usa, "Spatial"))
usa_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/usa_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(usa_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), USA")
dev.off()


# Test:
moran.mc(usa$origin_total,
         nb2listw(knn2nb(usa_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from Eritrea:

```{r}
eritrea <- df %>%
  filter(origin == "Eritrea") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

eritrea <- mun %>% dplyr::inner_join(eritrea, by = c("NAME_2"="municipality"))

eritrea_map <- tm_shape(eritrea) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Eritrea, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(eritrea_map, "../plots/Eritrea.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
eritrea_queen_nb <- poly2nb(eritrea$geometry, queen = TRUE)
eritrea_centers <- st_coordinates(st_centroid(eritrea$geometry))

# Saving the plot:
png("../plots/eritrea_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(eritrea_queen_nb, eritrea_centers, col = "red",add = TRUE)
title("Queen Contiguity, Eritrea")
dev.off()


# Test:
moran.mc(eritrea$origin_total, 
         nb2listw(eritrea_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
eritrea_centers_2 <- st_centroid(eritrea$geometry, of_largest_polygon = TRUE)
eritrea_nb_25km <- dnearneigh(eritrea_centers_2, 0, 25000)

# Saving the plot:
png("../plots/eritrea_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(eritrea_nb_25km, eritrea_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Eritrea")
dev.off()

# Test:
moran.mc(eritrea$origin_total, 
         nb2listw(eritrea_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
eritrea_nb_50km <- dnearneigh(eritrea_centers_2, 0, 50000)

# Saving the plot:
png("../plots/eritrea_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(eritrea_nb_50km, eritrea_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Eritrea")
dev.off()


# Test:
moran.mc(eritrea$origin_total, 
         nb2listw(eritrea_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
eritrea_nb_k3 <- knearneigh(eritrea_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(eritrea, "Spatial"))
eritrea_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/eritrea_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(eritrea_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Eritrea")
dev.off()

# Test:
moran.mc(eritrea$origin_total,
         nb2listw(knn2nb(eritrea_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from Australia:

```{r}
australia <- df %>%
  filter(origin == "Australia") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

australia <- mun %>% dplyr::inner_join(australia, by = c("NAME_2"="municipality"))

australia_map <- tm_shape(australia) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Australia, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
#tmap_save(australia_map, "../plots/Australia.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
australia_queen_nb <- poly2nb(australia$geometry, queen = TRUE)
australia_centers <- st_coordinates(st_centroid(australia$geometry))

# Saving the plot:
png("../plots/australia_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(australia_queen_nb, australia_centers, col = "red",add = TRUE)
title("Queen Contiguity, Australia")
dev.off()

# Test:
moran.mc(australia$origin_total, 
         nb2listw(australia_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
australia_centers_2 <- st_centroid(australia$geometry, of_largest_polygon = TRUE)
australia_nb_25km <- dnearneigh(australia_centers_2, 0, 25000)

# Saving the plot:
png("../plots/australia_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(australia_nb_25km, australia_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Australia")
dev.off()


# Test:
moran.mc(australia$origin_total, 
         nb2listw(australia_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
australia_nb_50km <- dnearneigh(australia_centers_2, 0, 50000)

# Saving the plot:
png("../plots/australia_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(australia_nb_50km, australia_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Australia")
dev.off()

# Test:
moran.mc(australia$origin_total, 
         nb2listw(australia_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
australia_nb_k3 <- knearneigh(australia_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(australia, "Spatial"))
australia_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/australia_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(australia_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Australia")
dev.off()

# Test:
moran.mc(australia$origin_total,
         nb2listw(knn2nb(australia_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```


### People coming from Poland:

```{r}
poland <- df %>%
  filter(origin == "Poland") %>%
  group_by(municipality) %>%
  summarise(origin_total = sum(n))

poland <- mun %>% dplyr::inner_join(poland, by = c("NAME_2"="municipality"))

poland_map <- tm_shape(poland) +
  tm_fill(col = "origin_total", title = "Total:",
          style = "quantile", n = 8) +
  tm_borders() +
  tm_layout(frame = TRUE,
            legend.show = TRUE,
            asp = 1.2,
            main.title = "Total number of Newcomers from Poland, 2020-2023",
            main.title.size = 1,
            main.title.position = "center",
            main.title.fontface = "bold")
  
tmap_save(poland_map, "../plots/Poland.png", width = 7, height = 5, dpi = 400, units = "in")
```

*Queen Contiguity:*

```{r}
set.seed(1)
poland_queen_nb <- poly2nb(poland$geometry, queen = TRUE)
poland_centers <- st_coordinates(st_centroid(poland$geometry))

# Saving the plot:
png("../plots/poland_queen.png", width = 800, height = 600)
plot(mun$geometry); plot(poland_queen_nb, poland_centers, col = "red",add = TRUE)
title("Queen Contiguity, Poland")
dev.off()


# Test:
moran.mc(poland$origin_total, 
         nb2listw(poland_queen_nb, style = "W",zero.policy=TRUE), 
         zero.policy=TRUE, nsim = 999)
```

*Distance of 25km:*

```{r}
set.seed(1)
poland_centers_2 <- st_centroid(poland$geometry, of_largest_polygon = TRUE)
poland_nb_25km <- dnearneigh(poland_centers_2, 0, 25000)

# Saving the plot:
png("../plots/poland_25km.png", width = 800, height = 600)
plot(mun$geometry); plot(poland_nb_25km, poland_centers_2, col = "red",add = TRUE)
title("Distance of 25km, Poland")
dev.off()


# Test:
moran.mc(poland$origin_total, 
         nb2listw(poland_nb_25km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Distance of 50km:*

```{r}
set.seed(1)
poland_nb_50km <- dnearneigh(poland_centers_2, 0, 50000)

# Saving the plot:
png("../plots/poland_50km.png", width = 800, height = 600)
plot(mun$geometry); plot(poland_nb_50km, poland_centers_2, col = "red",add = TRUE)
title("Distance of 50km, Poland")
dev.off()

# Test:
moran.mc(poland$origin_total, 
         nb2listw(poland_nb_50km, style = "W", zero.policy=TRUE),
         zero.policy=TRUE, nsim = 999)
```

*Three nearest neighbors:*

```{r}
set.seed(1)
poland_nb_k3 <- knearneigh(poland_centers_2, k = 3)

# Saving the plot:
coordinates_d <- coordinates(as(poland, "Spatial"))
poland_k3 <- knearneigh(coordinates_d, k = 3)
png("../plots/poland_k.png", width = 800, height = 600)
plot(mun$geometry); plot(knn2nb(poland_k3), coordinates_d, col = "red",add = TRUE)
title("K-nearest neighbors (k=3), Poland")
dev.off()


# Test:
moran.mc(poland$origin_total,
         nb2listw(knn2nb(poland_nb_k3), style = "W", zero.policy=TRUE),
         zero.policy=TRUE, 
         nsim = 999)
```



























