---
title: "Preprocessing"
author: "Justina Razanauskaite"
date: "2024-05-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages:

```{r}
pacman::p_load(tidyverse, readr)
```

Read the data in:

```{r}
df_2020 <- read.csv("../data/to_clean/2020.csv", 
                      sep = ";", 
                      header = FALSE, 
                      col.names = c("municipality", "origin", "n"), 
                      fileEncoding = "Windows-1252")

df_2021 <- read.csv("../data/to_clean/2021.csv", 
                      sep = ";", 
                      header = FALSE, 
                      col.names = c("municipality", "origin", "n"), 
                      fileEncoding = "Windows-1252")

df_2022 <- read.csv("../data/to_clean/2022.csv", 
                      sep = ";", 
                      header = FALSE, 
                      col.names = c("municipality", "origin", "n"), 
                      fileEncoding = "Windows-1252")

df_2023 <- read.csv("../data/to_clean/2023.csv", 
                      sep = ";", 
                      header = FALSE, 
                      col.names = c("municipality", "origin", "n"), 
                      fileEncoding = "Windows-1252")
```

The following code removes those rows that contain 0 as a number of newcomers from origin X to municipality Y. It also adds a column which represents the year of when data was collected, as in one of the following steps, all four datasets are combined into one:

```{r}
df_2020 <- df_2020[df_2020$n != 0, ]
df_2020$year <- 2020 

df_2021 <- df_2021[df_2021$n != 0, ]
df_2021$year <- 2021

df_2022 <- df_2022[df_2022$n != 0, ]
df_2022$year <- 2022 

df_2023 <- df_2023[df_2023$n != 0, ]
df_2023$year <- 2023 
```

Combine the data by rows:

```{r}
df <- rbind(df_2020, df_2021, df_2022, df_2023)
```

*Cleaning up:*
1. Removing rows that did not state any country of origin;
2. Removing rows that have two countries as an origin, just for simplicity;
3. Some countries were renamed so that the naming wouldn't affect the total numbers.

```{r}
sort(unique(df$origin))

df <- df[df$origin != "Africa not stated", ]
df <- df[df$origin != "Denmark", ]
df <- df[df$origin != "Asia not stated", ]
df <- df[df$origin != "Europe not stated", ]
df <- df[df$origin != "Middle East not stated", ]
df <- df[df$origin != "Not stated", ]
df <- df[df$origin != "Stateless", ]
df <- df[df$origin != "Yugoslavia, Federal Republic", ]
df <- df[df$origin != "Yugoslavia", ]
df <- df[df$origin != "Czechoslovakia", ]
df <- df[df$municipality != "Region Sjælland", ]
df <- df[df$municipality != "Serbia and Montenegro", ]

df[df$origin == "Congo, Democratic Republic", "origin"] <- "Congo"
df[df$origin == "Congo, Republic" , "origin"] <- "Congo"
df[df$origin == "Gambia, The", "origin"] <- "Gambia"
df[df$origin == "Republic of North Macedonia", "origin"] <- "Macedonia"
df[df$origin == "Soviet Union", "origin"] <- "Russia"
df[df$origin == "North Macedonia", "origin"] <- "Macedonia"
df[df$origin == "Timor-Leste (East Timor)", "origin"] <- "Timor-Leste"

```

Save the data:

```{r}
row.names(df) <- NULL
write.csv(df, "../data/df_final.csv")
```




